\documentclass[10pt,a4paper]{letter}
\usepackage[latin1]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}

%\address{Hiep H. Nguyen \\
%Institute of Research and Development\\
%Duy Tan University, P809 7/25 Quang Trung\\
%Danang 550000, Vietnam}

\signature{Huu Hiep Nguyen}

\begin{document}
\begin{letter}
{\large{\textbf{Human Resource Manager\\
Cinnamon AI Labs}}
}

\opening{Ladies and Gentlemen,}

I would like to introduce myself as an applicant for the part-time AI talent position at Cinnamon AI Labs, a leading AI solutions start-up in Southeast Asia. I am confident in my competence to perform as a part-time AI researcher at your company thanks to my extensive education and work experience.

During my work experience at Viettel RD (2011) and Duy Tan IRD (2017-now), I had an wide range of responsibilities including problem identification, solution design based on trade-off analysis, prototype construction and stepwise optimization. As a researcher, I was required to have excellent critical thinking skills, in-depth expertise in algorithm design and good programming ability in several popular languages such as Python/C++/Java.

My research ability rooted in my extensive education. I began with a bachelor's degree in computer science from Hanoi University of Science and Technology (2009), then a master's degree in IT convergence engineering from POSTECH (2013) and a Ph.D. in computer science from University of Lorraine (2016). Although my research interest is mainly about problems in data mining, I have good understanding of statistical learning methods as well. 

I believe my personality also plays a major role to succeed in this career path. I am an extremely analytical, data-oriented, and open-minded. 

I would like to thank you for taking the time to review my application. 
I look forward to hearing more about Cinnamon AI Labs and the details of the AI researcher position. 
I feel that my education and experience will ensure my success in this role.

\closing{Yours sincerely,}

%\cc{Cclist}
%\ps{adding a postscript}
%\encl{list of enclosed material}
\end{letter}
\end{document}
