%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Graduate Curriculum Vitae
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[margin, 10pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here

\usepackage{helvet} % Default font is the helvetica postscript font
%\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above

\usepackage[utf8]{inputenc}
%\usepackage[T1]{fontenc}
\usepackage[francais]{babel}


\setlength{\textwidth}{5.1in} % Text width of the document

\begin{document}


%----------------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------

\moveleft.5\hoffset\centerline{\large\bf Huu-Hiep NGUYEN} % Your name at the top
 
\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip % Horizontal line after name; adjust line thickness by changing the '1pt'
 
\moveleft.5\hoffset\centerline{A201, LORIA/INRIA Nancy} % Your address
\moveleft.5\hoffset\centerline{54000 Nancy, France}
\moveleft.5\hoffset\centerline{+330781783290}
\moveleft.5\hoffset\centerline{hienh.vtt@gmail.com}

%----------------------------------------------------------------------------------------

\begin{resume}

 
%\section{OBJECTIVE}  
%
%To obtain a career that will allow myself to take full advantage of my passion and experience in software engineering and computer science. 

\section{PERSONAL}
Date of birth: 21st April 1986 \\
Citizenship: Vietnam \\
Languages: English (fluent, IELTS: 7.5, TOEIC: 900), French (professional, DELF B2), Vietnamese (native)

\section{RESEARCH INTERESTS}
Data Privacy (differential privacy, location privacy) \\
Social Network Analysis \\
Game Theory \\
Cryptography

\section{EDUCATION}

{\sl University of Lorraine}  \hfill Oct 2013 - Oct 2016 \\
PhD in Computer Science \\
INRIA/LORIA Nancy, France \\
{\sl PhD thesis:} Social Graph Anonymization

% 
{\sl Pohang University of Science and Technology (POSTECH)}  \hfill Aug 2011 - Jun 2013 \\
Master of Science in IT Convergence Engineering (ITCE), POSTECH, Pohang, Korea \\
{\sl GPA: 4.09} \\
{\sl Master thesis:} Linear Counting Queries under Differential Privacy: A Comparative Study

%
{\sl Hanoi University of Science and Technology (HUST)}  \hfill Aug 2004 - Jun 2009 \\
Franco-Vietnamese Program for Training Excellent Students (PFIEV) \\
{\sl GPA: 8.48 /10} \\
Addendum of Engineer Certificate co-issued by HUST and INP Grenoble, France \\
{\sl Bachelor thesis:} Building Self-care Tool for UPnP DM Devices Using Web 2.0

 
\section{AWARDS}
Best Paper Award at FPS 2014, Montreal, Canada											\hfill 2014 \\
INRIA Scholarship																		\hfill 2013 - 2016 \\
POSTECH Scholarship																		\hfill 2011 - 2013 \\
Ministry of Education and Training Scholarship for Excellent Students 					\hfill 2004 - 2009 \\
Second Prize in National Mathematics Competition for gifted students					\hfill 2004 \\
Third Prize in National Informatics Competition for gifted students						\hfill 2003 


\section{JOURNAL ARTICLES}
\textbf{Hiep H. Nguyen}, Abdessamad Imine, Michael Rusinowitch. \textit{Network Structure Release under Differential Privacy}. Transactions on Data Privacy, 2016. (under 1st revision) \\
\textbf{Hiep H. Nguyen}, Jong Kim, Yoonho Kim. \textit{Differential Privacy in Practice}. Journal of Computing Science and Engineering, 2013.

\section{CONFERENCE ARTICLES}
\textbf{Hiep H. Nguyen}, Abdessamad Imine, Michael Rusinowitch. \textit{Differentially Private Publication of Social Graphs at Linear Cost}. ASONAM 2015, Paris, France. \\
\textbf{Hiep H. Nguyen}, Abdessamad Imine, Michael Rusinowitch. \textit{Anonymizing Social Graphs via Uncertainty Semantics}. ASIACCS 2015, Singapore. \\
\textbf{Hiep H. Nguyen}, Abdessamad Imine, Michael Rusinowitch. \textit{A Maximum Variance Approach for Graph Anonymization}. FPS 2014, Montreal, Canada (\textbf{Best Paper Award}). \\
\textbf{Hiep H. Nguyen}, Abdessamad Imine, Michael Rusinowitch. \textit{Enforcing Privacy in Decentralized Mobile Social Networks}. ESSoS Doctoral Symposium 2014, Munich, Germany. \\
\textbf{Hiep H. Nguyen}, Ahmed Mehaoua, James Won-Ki Hong. \textit{Secure medical tele-consultation based on voice authentication and realtime audio/video encryption}. Ubi-HealthTech 2013, Jinhua, China.

\section{WORKSHOP PAPERS}
\textbf{Hiep H. Nguyen}, Abdessamad Imine, Michael Rusinowitch. \textit{Community Detection under Differential Privacy} WPES 2016. (under review). \\
\textbf{Hiep H. Nguyen}, Abdessamad Imine, Michael Rusinowitch. \textit{Private Link Exchange over Social Graphs} WPES 2016. (under review). \\
\textbf{Hiep H. Nguyen}, Dongju Chae, Jangwoo Kim, Jong Kim. \textit{MeshCloak: A Map-Based Location Privacy Model for Continuous Query in Mobile Services}. WAIS 2013, Nagasaki, Japan.



\section{RESEARCH EXPERIENCE}

\textbf{PESTO Team, LORIA/INRIA Nancy} \hfill Oct 2013 - Oct 2016 \\
conducted research on Graph Anonymization.	

\textbf{High Performance Computing Lab (HPC)}	\hfill Aug 2011 - Jun 2013 \\
conducted research on Differential Privacy.	\\
conducted research on Location Privacy. \\
developed a solution for Secure Medical Tele-consultation. 



\section{INDUSTRY EXPERIENCE}

%{\sl Software Engineer} \hfill June 2015 - Present \\
%Ionic Security Inc, Atlanta, GA
%\begin{itemize}
%\item Deployed standardization techniques throughout a large codebase.
%\item Developed and designed a large AngularJS web application.
%\item Leveraged Golang's compiled nature to simplify deployments and decrease ops issues.
%\item Developed and maintained the development environment used by front end software engineers.
%\item Developed a distributed authentication and routing system for a SOA using Golang, Nginx, and Lua.
%\item Integrated the Jenkins Continuous Integration(CI) systems into the existing deployment processes.
%\item Implemented web application security standards defined by OWASP.
%\end{itemize} 
%
%{\sl Software Engineer} \hfill August 2013 - June 2015 \\
%Georgia Tech Research Institute, Electronic Systems Laboratory, Atlanta, GA 
%\begin{itemize} \itemsep -2pt % Reduce space between items
%\item Designed and developed Django/AngularJS software systems for the Department of Defense, Army, and Navy.
%\item Presented software demos to Department of Defense derived clients.
%\end{itemize}
% 
%{\sl Independent Software Contractor} \hfill May 2014 - February 2016\\
%JTE Technologies, Atlanta, GA
%\begin{itemize} 
%\item Performed the full software development process with the end result of deploying a large scale software system that manages access to high priority physical and logical assets.
%\item Designed the architecture for a Django/AngularJS software system.
%\end{itemize} 



\textbf{Viettel R\&D} (Viettel Group)		\hfill Feb 2011 - Jul 2011 \\
conducted research on Radar data fusion and applications.

\textbf{Viettel Technologies}. (Viettel Group)		\hfill Oct 2009 - Jan 2011 \\
developed the SMS Banking System for Mekong Housing Bank (Vietnam). \\
designed the XPAY electronic-payment system (Viettel). \\
participated in the appraisal team of CMMi Level 3 for Viettel Technologies.

\textbf{Orange Labs} (Grenoble, France)			\hfill Jan 2009 - May 2009 \\
4-month internship \\
built a self-care tool for testing Universal Plug and Play Device Management profile (UPnP DM) by using Web 2.0 (Dojo, Comet), OSGi. \\


\section{TECHNICAL SKILLS}

\begin{table}[h]
\begin{tabular}{ll}
Programming languages & C/C++, Java, Python, MATLAB, C\# \\
Mobile OSes &	Android \\
Frameworks & 	.NET, J2EE, Spring, Hibernate, Struts, Web-service, OSGi \\
Methodologies & CMMi DEV v1.2, UML, Design Patterns. \\
Databases &	Oracle, MS SQL Server, MySQL, PostgreSQL. \\
IDEs & 		Eclipse, Visual Studio. \\
\end{tabular}
\end{table}

\pagebreak
\section{COURSES}
\begin{table}[h]
\begin{tabular}{ll}
EECE700A & Data Mining \\ 
ITCE 605 & Network and Service Management \\
ITCE701B & Convergence Using Smart Phones and Devices \\
ITCE701C & Dependable Computing \\
EECE515  & Machine Learning \\
ITCE500	 & Introduction to IT Convergence Engineering \\
ITCE600  & Applications of IT Convergence Engineering \\
EMMA 22  & Heat conduction : From macro to micro \\
EMMA 07  & Introduction aux simulations numériques \\
Fi4 223  & Résidentiel DCCE 2eme A (innovation pédagogique) \\
\end{tabular}
\end{table}


\section{EXTRA-CURRICULAR \\ ACTIVITIES} 
\textit{Association of Vietnamese Students in Nancy-Metz}, France, \hfill 2014 - 2016\\
Board of Execution, in charge of sport activities.

 

\section{REFERENCES}
\textbf{Dr. Micha\"{e}l Rusinowitch} \\
\textit{(PhD advisor)} \\
Directeur de recherche (Research Director) \\
A209 LORIA/INRIA Nancy - Grand Est 615 rue du Jardin Botanique \\
Tel: +33 (0)3 83 59 30 20 \\
Email: michael.rusinowitch@loria.fr


\textbf{Dr. Abdessamad Imine} \\
\textit{(PhD co-advisor)} \\
Maître de conférences (Associate Professor) \\
A205 LORIA/INRIA Nancy - Grand Est 615 rue du Jardin Botanique \\
Tel/Fax: +33 (0)3 54 95 85 35/ +33 (0)3 83 27 83 19 \\
Email: abdessamad.imine@loria.fr


\textbf{Dr. Jong Kim} \\
\textit{(Master advisor)} \\
Director, Center for Mobile Embedded Software Technology \\
Professor, Dept. of Computer Science and Engineering \\
Pohang University of Science and Technology (POSTECH), Pohang, Korea \\
Tel/Fax: +82 54 279 2257/ +82 54 279 2299 \\
Email: jkim@postech.ac.kr  


\textbf{Dr. Jangwoo Kim} \\
\textit{(Master co-advisor)} \\
Associate Professor, Dept. of Computer Science and Engineering \\
Pohang University of Science and Technology (POSTECH), Pohang, Korea \\
Tel/Fax: +82 54 279 2390/ +82 54 279 2299 \\
Email: jangwoo@postech.ac.kr 




\end{resume}
\end{document}